My title

### 2024-12-01 paper/paper.qmd
Finished making graphs

---
title: "My title"
subtitle: "An analysis of solved and unsolved homicides from 2007 to 2017 in the United States's 2 largest cities"
author: 
  - Emily Su
thanks: "Code and data are available at: [https://github.com/moonsdust/unsolved-murders](https://github.com/moonsdust/unsolved-murders)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format:
  pdf:
    toc: true
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(arrow)
library(ggplot2)
library(modelsummary)
library(rstanarm)

@@

@@

@@

Our results are summarized in @tbl-modelresults.

## Model Results {#sec-model-results}
```{r}
#| label: tbl-model-result
#| tbl-cap: Relationship between a homicide being unsolved from 2007 to 2017 with the city and date (month, year) a victim is found in/on and the race, age, and sex of a victim with their mean absolute deviation (MAD) values in parenthesis    
#| echo: false
#| warning: false
#| message: false

modelsummary(
  # List out unsolved_model_results information
  list("Unsolved homicides (2007 to 2017)" = unsolved_model_results),
  # Specify MAD as the statistic
  statistic = "mad"
)
```

```{r}
#| label: fig-model-result-ci
#| fig-cap: The credible intervals (line) for coefficient estimates (dot) of predictors of homicides that go unsolved from 2007 to 2017
#| echo: false
#| warning: false
#| message: false
# Specify credible interval to be 90% and present model results
modelplot(unsolved_model_results, conf_level = 0.9) +
  labs(x = "90 per cent credible interval")
```

# Discussion {#sec-discussion}

@@

# Appendix {-}

# Surveys, sampling, and observational data (To be changed)

# Model details {#sec-model-details}

## Posterior predictive check

@@

## Diagnostics

>>>>

---
title: "My title"
subtitle: "An analysis of solved and unsolved homicides from 2010 to 2017 in the United States's 2 largest cities, New York and Los Angeles"
author: 
  - Emily Su
thanks: "Code and data are available at: [https://github.com/moonsdust/unsolved-murders](https://github.com/moonsdust/unsolved-murders)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format:
  pdf:
    toc: true
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(arrow)
library(ggplot2)
library(modelsummary)
library(rstanarm)
library(dplyr)
library(knitr)

@@

This led to us investigate the following question in our paper: what are the differences in homicide case information like the year and city the homicide took place and the victims’ perceived characteristics (age, sex, and race) between solved and unsolved homicides in 2 of the largest cities in the United States, New York and Los Angeles, from 2010 to 2017?

@@

Limitation of dataset. 
- There’s only data available from 2010 onwards for both New York and Los Angeles 
- Not all victims were able to be identified and they were removed from the dataset during data cleaning

@@

## Differences in Homicide Case Information Between Solved and Unsolved Cases in New York and Los Angeles (2010 to 2017)

### Date (Month and Year)
```{r}
#| label: fig-month-bar
#| fig-cap: "Number of solved and unsolved homicides across the 12 months of a year in Los Angeles and New York (2010 to 2017)"
#| echo: false
#| warning: false
#| message: false

number_of_cases_month <- 
  analysis_data_homicides |>
  # Group by solved and unsolved homicides 
  group_by(arrest_was_not_made) |>
  # Count number of solved and unsolved homicides for each month
  count(month)|>
  # Rename count column
  rename(
    "num_of_cases_month" = n
  ) |>
  mutate(
    month = case_when(
      (month == 1) ~ "Jan",
      (month == 2) ~ "Feb",
      (month == 3) ~ "Mar",
      (month == 4) ~ "Apr",
      (month == 5) ~ "May",
      (month == 6) ~ "Jun",
      (month == 7) ~ "Jul",
      (month == 8) ~ "Aug",
      (month == 9) ~ "Sep",
      (month == 10) ~ "Oct",
      (month == 11) ~ "Nov",
      (month == 12) ~ "Dec",
      TRUE ~ "None")
  ) |>
  mutate(
    arrest_was_not_made = case_when(
      (arrest_was_not_made == 1) ~ "Arrest was not made",
      (arrest_was_not_made == 0) ~ "Arrest was made",
      TRUE ~ "None")
  )

# To sort month in certain order 
# Referenced: https://www.geeksforgeeks.org/how-to-put-x-axis-in-order-month-in-r/ for code
number_of_cases_month$month <- factor(number_of_cases_month$month, levels = c('Jan', 'Feb', 'Mar', 'Apr', 'May', 'Jun', 'Jul', 'Aug', 'Sep', 'Oct', 'Nov', 'Dec'))

number_of_cases_month |>
  ggplot(mapping = aes(x = month, y = num_of_cases_month)) +
  # Creates two graphs based on the status of the case
  facet_wrap(facets = vars(arrest_was_not_made), dir = "v") +
  geom_bar(stat = "identity", fill = "#936639") +
  theme_minimal() +
  labs(x = "Month of the year", y = "Number of homicide cases") +
  theme(legend.position = "bottom")
```

```{r}
#| label: tbl-month-table
#| tbl-cap: "Number of solved and unsolved homicides across the 12 months of a year in Los Angeles and New York (2010 to 2017)"
#| echo: false
#| warning: false
#| message: false

# Create table for the number of cases per month
number_of_cases_month |>
  rename(
    "Month" = month,
    "Status of the homicide case" = arrest_was_not_made,
    "Number of cases in the month" = num_of_cases_month
  ) |>
  kable()
```

```{r}
#| label: fig-year-bar
#| fig-cap: "Number of solved and unsolved homicides from 2010 to 2017 in Los Angeles and New York"
#| echo: false
#| warning: false
#| message: false

number_of_cases_year <- 
  analysis_data_homicides |>
  # Group by solved and unsolved homicides 
  group_by(arrest_was_not_made) |>
  # Count number of solved and unsolved homicides for each year
  count(year)|>
  # Rename count column
  rename(
    "num_of_cases_year" = n
  ) |>
  mutate(
    arrest_was_not_made = case_when(
      (arrest_was_not_made == 1) ~ "Arrest was not made",
      (arrest_was_not_made == 0) ~ "Arrest was made",
      TRUE ~ "None")
  )

number_of_cases_year |>
  ggplot(mapping = aes(x = as.character(year), y = num_of_cases_year)) +
  # Creates two graphs based on the status of the case
  facet_wrap(facets = vars(arrest_was_not_made), dir = "v") +
  geom_bar(stat = "identity", fill = "#936639") +
  theme_minimal() +
  labs(x = "Year", y = "Number of homicide cases") +
  theme(legend.position = "bottom")
```

```{r}
#| label: tbl-year-table
#| tbl-cap: "Number of solved and unsolved homicides from 2010 to 2017 in Los Angeles and New York"
#| echo: false
#| warning: false
#| message: false

# Create table for dataframe pertaining to the number of cases per year
number_of_cases_year |>
  rename(
    "Year" = year,
    "Status of the homicide case" = arrest_was_not_made,
    "Number of cases in the year" = num_of_cases_year
  ) |>
  kable()
```

### City

```{r}
#| label: fig-city-bar
#| fig-cap: "Proportion of solved and unsolved homicides in Los Angeles and New York (2010 to 2017)"
#| echo: false
#| warning: false
#| message: false

number_of_cases_city <- 
  analysis_data_homicides |>
  # Group by city 
  group_by(city) |>
  # Count number of solved and unsolved homicides for each city
  count(arrest_was_not_made)|>
  # Rename count column
  rename(
    "num_of_cases_city" = n
  ) |>
  mutate(
    "proportion_of_cases" = round(num_of_cases_city/sum(num_of_cases_city), 2)
  ) |>
  mutate(
    arrest_was_not_made = case_when(
      (arrest_was_not_made == 1) ~ "Arrest was not made",
      (arrest_was_not_made == 0) ~ "Arrest was made",
      TRUE ~ "None")
  )

number_of_cases_city |>
  ggplot(mapping = aes(x = arrest_was_not_made, y = proportion_of_cases)) +
  # Creates two graphs based on the status of the case
  facet_wrap(facets = vars(city), dir = "v") +
  geom_bar(stat = "identity", fill = "#936639") +
  theme_minimal() +
  labs(x = "Status of the homicide case", y = "Proportion of cases") +
  theme(legend.position = "bottom")
```
```{r}
#| label: tbl-city-table
#| tbl-cap: "Proportion and number of solved and unsolved homicides in Los Angeles and New York (2010 to 2017)"
#| echo: false
#| warning: false
#| message: false

number_of_cases_city |>
  rename(
    "City" = city, 
    "Status of the homicide case" = arrest_was_not_made,
    "Proportion of cases" = proportion_of_cases,
    "Number of cases" = num_of_cases_city
  ) |>
  kable()
```

### Disposition
```{r}
#| label: fig-disposition-bar
#| fig-cap: "Disposition of homicide cases in New York and Los Angeles (2010 to 2017)"
#| echo: false
#| warning: false
#| message: false

number_of_dispositions_city <- 
  analysis_data_homicides |>
  # Group by city 
  group_by(city) |>
  # Count number of dispositions for each city
  count(disposition)|>
  # Rename count column
  rename(
    "num_of_disposition_city" = n
  )

number_of_dispositions_city |>
  ggplot(mapping = aes(x = disposition, y = num_of_disposition_city)) +
  # Creates two graphs based on the status of the case
  facet_wrap(facets = vars(city), dir = "v") +
  geom_bar(stat = "identity", fill = "#936639") +
  theme_minimal() +
  labs(x = "Disposition of homicide", y = "Number of cases") +
  theme(legend.position = "bottom")
```

```{r}
#| label: tbl-disposition-table
#| tbl-cap: "Disposition of homicide cases in New York and Los Angeles (2010 to 2017)"
#| echo: false
#| warning: false
#| message: false

# Create table for dataframe pertaining to the number of cases per year
number_of_dispositions_city |>
  rename(
    "City" = city,
    "Disposition of the homicide case" = disposition,
    "Number of cases" = num_of_disposition_city
  ) |>
  kable()
```

### Victim's Age 
```{r}
#| label: fig-victim-age-histogram
#| fig-cap: "Distribution of victim's age in solved and unsolved homicides in New York and Los Angeles (2010 to 2017)"
#| echo: false
#| warning: false
#| message: false

victim_age_dataframe <- 
  analysis_data_homicides |>
  # Group by age 
  group_by(victim_age) |>
  # Count number of solved and unsolved homicides by age
  count(arrest_was_not_made)|>
  # Rename count column
  rename(
    "num_of_cases" = n
  ) |>
  mutate(
    arrest_was_not_made = case_when(
      (arrest_was_not_made == 1) ~ "Arrest was not made",
      (arrest_was_not_made == 0) ~ "Arrest was made",
      TRUE ~ "None")
  )

# Referenced Telling Stories with Data by Rohan Alexander for histogram code: https://tellingstorieswithdata.com/05-graphs_tables_maps.html#histograms
victim_age_dataframe |>
  ggplot(aes(x = victim_age, fill = arrest_was_not_made)) +
  geom_histogram(position = "dodge") +
  theme_minimal() +
  scale_fill_manual(values=c("#936639", "#c2c5aa")) +
  labs(
    x = "Age of victim",
    y = "Number of cases",
    fill = "Status of homicide"
  ) +
  theme(legend.position = "bottom")
```

### Victim's Sex
```{r}
#| label: fig-victim-sex-bar
#| fig-cap: "Proportion of homicide cases per sex in New York and Los Angeles (2010 to 2017)"
#| echo: false
#| warning: false
#| message: false

number_of_cases_victim_sex <- 
  analysis_data_homicides |>
  # Group by victim's sex 
  group_by(victim_sex) |>
  # Count number of solved and unsolved homicides for each sex
  count(arrest_was_not_made)|>
  # Rename count column
  rename(
    "num_of_cases_victim_sex" = n
  ) |>
  mutate(
    "proportion_of_cases" = round(num_of_cases_victim_sex/sum(num_of_cases_victim_sex), 2)
  ) |>
  mutate(
    arrest_was_not_made = case_when(
      (arrest_was_not_made == 1) ~ "Arrest was not made",
      (arrest_was_not_made == 0) ~ "Arrest was made",
      TRUE ~ "None")
  )

number_of_cases_victim_sex |>
  ggplot(mapping = aes(x = victim_sex, y = proportion_of_cases)) +
  # Creates two graphs based on the status of the case
  facet_wrap(facets = vars(arrest_was_not_made), dir = "v") +
  geom_bar(stat = "identity", fill = "#a4ac86") +
  theme_minimal() +
  labs(x = "Victim's Sex", y = "Proportion of cases") +
  theme(legend.position = "bottom")
```

```{r}
#| label: tbl-victim-sex-table
#| tbl-cap: "Proportion and number of homicide cases per sex in New York and Los Angeles (2010 to 2017)"
#| echo: false
#| warning: false
#| message: false

number_of_cases_victim_sex |>
  rename(
    "Victim's sex" = victim_sex, 
    "Status of the homicide case" = arrest_was_not_made,
    "Proportion of cases" = proportion_of_cases,
    "Number of cases" = num_of_cases_victim_sex
  ) |>
  kable()
```

### Victim's Race 
```{r}
#| label: fig-victim-race-bar
#| fig-cap: "Number of homicide cases per race in New York and Los Angeles (2010 to 2017)"
#| echo: false
#| warning: false
#| message: false

number_of_cases_victim_race <- 
  analysis_data_homicides |>
  # Group by victim's race 
  group_by(victim_race) |>
  # Count number of solved and unsolved homicides for each race
  count(arrest_was_not_made)|>
  # Rename count column
  rename(
    "num_of_cases_victim_race" = n
  ) |>
  mutate(
    arrest_was_not_made = case_when(
      (arrest_was_not_made == 1) ~ "Arrest was not made",
      (arrest_was_not_made == 0) ~ "Arrest was made",
      TRUE ~ "None")
  )

number_of_cases_victim_race |>
  ggplot(mapping = aes(x = victim_race, y = num_of_cases_victim_race)) +
  # Creates two graphs based on the status of the case
  facet_wrap(facets = vars(arrest_was_not_made), dir = "v") +
  geom_bar(stat = "identity", fill = "#a4ac86") +
  theme_minimal() +
  labs(x = "Victim's Race", y = "Number of cases") +
  theme(legend.position = "bottom")
```
```{r}
#| label: tbl-victim-race-table
#| tbl-cap: "Number of homicide cases per sex in New York and Los Angeles (2010 to 2017)"
#| echo: false
#| warning: false
#| message: false

number_of_cases_victim_race |>
  rename(
    "Victim's race" = victim_race, 
    "Status of the homicide case" = arrest_was_not_made,
    "Number of cases" = num_of_cases_victim_race
  ) |>
  kable()
```

\newpage
## Model Results {#sec-model-results}
```{r}
#| label: tbl-model-result
#| tbl-cap: Relationship between a homicide being unsolved from 2010 to 2017 with the city and year a victim is found in/on and the race, age, and sex of a victim. Mean absolute deviation (MAD) values are in parenthesis.
#| echo: false
#| warning: false
#| message: false

modelsummary(
  # List out unsolved_model_results information
  list("Unsolved homicides (2010 to 2017)" = unsolved_model_results),
  # Specify MAD as the statistic
  statistic = "mad"
)
```

```{r}
#| label: fig-model-result-ci
#| fig-cap: The credible intervals (line) for coefficient estimates (dot) of predictor variables for homicides that go unsolved from 2010 to 2017.
#| echo: false
#| warning: false
#| message: false
# Specify credible interval to be 90% and present model results
modelplot(unsolved_model_results, conf_level = 0.9) +
  labs(x = "90 per cent credible interval")
```

\newpage
# Discussion {#sec-discussion}

@@

# Appendix {#sec-appendix}

## Surveys, sampling, and observational data (To be changed)

## Model details {#sec-model-details}

### Posterior predictive check

@@

### Diagnostics
